Soundness Proof for Eliminating Malloc-Recycle Data Races in Stateless Model Checking

### 2015-11-02 pldi-16/di.tex
Talk about cli/sti which I still need to actually implement.

We chose \landslide~\cite{landslide} as our stateless model checker due to its ability to trace program execution at the granularity of individual instructions and memory accesses, which dynamic data-race detection requires.
\landslide~features DPOR,
%\cite{dpor},
state space estimation, and a hybrid lockset/happens-before data-race analysis.
It avoids state space cycles (e.g. ad-hoc synchronization with {\tt yield()} or even {\tt xchg} loops) with a heuristic similar to Fair-Bounded Search \cite{bpor}. % TODO: devote a paragraph to this, after talking about drs in locks
% this line can be cut if space is needed
It can test both user- and kernel-level code, although is limited to timer-driven nondeterminism.
Its bug-detection metrics include assertion failure, deadlock, segfault, heap checking (like Valgrind~\cite{valgrind}), and a heuristic infinite loop/livelock check.

@@

\quicksand~is an independent program that wraps the execution of several \landslide~instances.
The implementation is roughly 3000 lines of C.
It uses a thread pool to schedule the available state spaces,
sorting such jobs according to their status among a running queue, pending queue, and suspended queue.
Jobs are further prioritized by number of PPs, ETA, and whether they include data-race PPs.
We seed the exploration with the four subsets of ``hard-coded'' locking API PPs shown in Figure~\ref{fig:id}.

>>>>

We chose \landslide~\cite{landslide} as our stateless model checker due to its ability to trace program execution at the granularity of individual instructions and memory accesses, which dynamic data-race detection requires.
\landslide~features DPOR,
%\cite{dpor},
state space estimation, and a hybrid lockset/happens-before data-race analysis.
% TODO: \cite{fairstatelessmc} instead or in addition?
It avoids state space cycles (e.g. ad-hoc synchronization with {\tt yield()} or even {\tt xchg} loops) with a heuristic similar to Fair-Bounded Search \cite{bpor}. % TODO: devote a paragraph to this, after talking about drs in locks
% this line can be cut if space is needed
It can test both user- and kernel-level code, although is limited to timer-driven nondeterminism.
Its bug-detection metrics include assertion failure, deadlock, segfault, heap checking (like Valgrind~\cite{valgrind}), and a heuristic infinite loop/livelock check.

@@

\quicksand~is an independent program that wraps the execution of several \landslide~instances.
The implementation is roughly 3000 lines of C.
It uses a thread pool to schedule the available state spaces,
sorting such jobs according to their status among a running queue, pending queue, and suspended queue.
Jobs are further prioritized by number of PPs, ETA, and whether they include data-race PPs.

{\bf Initial PPs.}
For testing user-space code, we seed the exploration with the four subsets of ``hard-coded'' locking API PPs shown in Figure~\ref{fig:id}.
By extension, these also introduce preemptions on any other sync primitives implemented with mutexes,
such as condvars, semaphores, and r/w locks.

For kernel-level testing, we consider interrupt-disabling to be analogous to locking,
so we also preempt just before {\tt cli} and just after {\tt sti}\footnote{
During data-race detection, {\tt cli}/{\tt sti} are treated as a single global lock,
as {\tt cli}'d memory accesses can still race with others that have interrupts on.}.
% FIXME: "What happened to yield?" "Yield is implicitly included in each subset."
\quicksand~is configured to use the subsets
$\{ \}$,
$\{lock\}$,
$\{unlock\}$,
$\{cli\}$,
$\{sti\}$,
and $\{lock,unlock,cli,sti\}$.
Other subsets are obviously possible, but as a heuristic, we don't bother with them.
